Exploring_symptoms_across_cohorts

### 2022-10-27 characterisation/Code/Comparing_symptoms.Rmd
updates

```{r include=FALSE}
# packages
library(SqlRender)
library(DBI)
library(DatabaseConnector)
library(here)
library(dplyr)
library(tidyr)
library(CDMConnector)
library(stringr)
library(lubridate)
library(gtsummary)

@@

@@

```{r include=FALSE}
generate_table <- function(cohort_id, window, name){
data <- cdm$er_long_covid_all_symptoms_cohorts %>%
  filter(main_cohort_id == cohort_id & window_days == window) %>%
  collect()
summary <-  data%>% 
  mutate(all_symp = as.factor(all_symp)) %>%
  select(-subject_id, -window_days, - main_cohort_id, - cohort_start_date ) %>%
  mutate(gen = paste0(name)) %>%
   tbl_summary(
       by = "gen",
  digits = all_categorical()~ c(0,1),
  missing = "ifany",
  missing_text= "Missing",
  percent = "col"
           ) %>% 
  bold_labels()
  summary
}
```

```{r include=FALSE}
t.covid.infection <- generate_table(cohort_id= "22",
                                    window="90",
                                    name = "New COVID-19 infection")

@@

t.covid.confirmed <- generate_table(cohort_id= "30",
                                    window="90",
                                    name = "Confirmed infections")

t.tested.negative.earliest <- generate_table(cohort_id = "29",
                                    window="90",
                                    name = "Tested negative, earliest")

t.pcr.negative.earliest <- generate_table(cohort_id = "24",
                                    window="90",
                                    name = "PCR negative, earliest")

>>>>

```{r include=FALSE}
# packages
library(SqlRender)
library(DBI)
library(DatabaseConnector)
library(here)
library(dplyr)
library(tidyr)
library(CDMConnector)
library(stringr)
library(lubridate)
library(gtsummary)
library(tableone)

@@

#  get ids for cohorts

cohorts_ids  <- read.csv2(here("ATLAS Cohort Definitions_LongCovid.csv")) %>%
                          mutate(name= paste(sub(".*LongCov-ER_", "", name)))

new_infection_id <- as.character(cohorts_ids %>%
                    filter(str_detect(name, "New_Infection")) %>% 
                    select(cohort_definition_id) %>% pull())

tested_positive_id <- as.character(cohorts_ids %>%
                    filter(str_detect(name, "Tested_Positive")) %>% 
                    select(cohort_definition_id) %>% pull())

tested_negative_earliest_id <- as.character(cohorts_ids %>%
                    filter(str_detect(name, "Tested_Negative_earliest")) %>% 
                    select(cohort_definition_id) %>% pull())

pcr_negative_earliest_id <-as.character( cohorts_ids %>%
                    filter(str_detect(name, "PCR_Negative_earliest")) %>% 
                    select(cohort_definition_id) %>% pull())

# get data for table 1
 table1_data_new_infections  <- load(here("data", "table1_data_new_infections.Rda")))

@@

table1.data<-rbind(  
# those without missing values
       table1_data_new_infections   %>%
        mutate(group = "With COVID-19_infection"),
        table1_data_new_infections  %>%
        filter(long_covid == 1)%>%
          mutate(group = "90 days Long Covid symtpoms"))

# variables
vars<-c(
        "age",
        "age_gr2",
        "gender",
        "nationality_cat",
        "vaccination_status",
        "medea",
        "asthma",
        "autoimmune_disease",
        "copd",
        "dementia",
        "diabetes",
        "heart_disease",
        "cancer",
        "hypertension",
        "renal_impairment"
)

factor.vars<- c(
        "age_gr2",
        "gender",
        "nationality_cat",
        "vaccination_status",
        "medea",
        "asthma",
        "autoimmune_disease",
        "copd",
        "dementia",
        "diabetes",
        "heart_disease",
        "cancer",
        "hypertension",
        "renal_impairment"
)

summary.characteristics<-print(CreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=T,
  data = table1.data,
  strata=c("group"),
  test = F), 
  showAllLevels=F,
  smd=T,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  contDigits = 1,
  printToggle=FALSE)

# format numbers (eg commas etc)  
# functionality does not seem to be in tableone package
# so do this manually
for(i in 1:2) {
# tidy up 
  cur_column <- summary.characteristics[, i]
  cur_column <- str_extract(cur_column, '[0-9.]+\\b') %>% 
                as.numeric() 
  cur_column <-nice.num(cur_column)
  # add back in
  summary.characteristics[, i] <- str_replace(string=summary.characteristics.loss[, i], 
                              pattern='[0-9.]+\\b', 
                              replacement=cur_column)    
}

```{r include=FALSE}
# function to obtain data for table
generate_table <- function(cohort_id, window, name){
data <- cdm$er_long_covid_all_symptoms_cohorts %>%
  filter(main_cohort_id == cohort_id & window_days == window) %>%
  distinct() %>%
  collect()
summary <-  data%>% 
  mutate(all_symp = as.factor(all_symp)) %>%
  select(-subject_id, -window_days, - main_cohort_id, - cohort_start_date ) %>%
  mutate(gen = paste0(name)) %>%
   tbl_summary(
       by = "gen",
  digits = all_categorical()~ c(0,1),
  missing = "ifany",
  missing_text= "Missing",
  percent = "col"
           ) %>% 
  bold_labels()
  summary
}
```

```{r include=FALSE}
t.covid.infection <- generate_table(cohort_id= new_infection_id,
                                    window="90",
                                    name = "New COVID-19 infection")

@@

t.covid.confirmed <- generate_table(cohort_id= tested_positive_id,
                                    window="90",
                                    name = "Confirmed infections")

t.tested.negative.earliest <- generate_table(cohort_id = tested_negative_earliest_id,
                                    window="90",
                                    name = "Tested negative, earliest")

t.pcr.negative.earliest <- generate_table(cohort_id = pcr_negative_earliest_id,
                                    window="90",
                                    name = "PCR negative, earliest")
